\documentclass{article}
% !TeX spellcheck = en_US 
\usepackage[margin=2cm]{geometry}
\usepackage{makecell}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage[shortlabels]{enumitem}
\usepackage[bottom]{footmisc}
\usepackage{verbatim}
\usepackage[english]{babel}
\usepackage{lscape}

\begin{comment}
Grades from previous iterations:
Iteration 1:
UC1 (A1): 6
UC2 (B1): 6
UC3 (C1): 5
DM: 7
Rest: 9

Iteration 2:
DM: 6 <- what went wrong here
CD: 5
UC4/A2: 5
UC5/B2: 6
UC6/C2: 7
SD1/A1: 7 (by Nicu)
SD2/B1: 9 (by Robbin) <- see what was so good about this one and replicate
SD3/C1: 7 (by Nicu)
SD4/A2: 0 (thanks oli)
SD5/B2: 0 (thanks oli)
SD6/C2: 5 (by Robbin)
General Impression: 8

TODOs
All:
 - Name design considerations for the DM
 - Update user wishes, stories and the like to fit the new requirements
 - Power tree and Domain Model need updating according to the new requirements
 - In the class diagram, make sure all visibility is logical (currently, everything is public, marked with +.) See slides for definitions of +, -, #, ~ etc...
 - Add an auction object to DM
 - Consider adding the following classes to the class diagram: 
 	mailing list (physical address), emailing list (digital address), Item categories, ?notification/email?, 

Robbin:
 - Add item to catalogue list in addItem
 - explain police and idividual item list in dm
 - explain why there is no normal customer in dm
 - change gb and wb B1 to use modifyItem() function (name change)
 - dm: auction data in item maybe replace by association with auction?
  
Nicu:
 - C2 SSD still has user instead of actor
 - Update SSD
 - Specify in UC title what you are deleting
 - One UC should specify one session. YOu might delete more than 1 item per session
 - Honestly, just check the pictures. There's so many comments and remarks.
 - For SSD, instead of e.g. ``answered yes'', you could do b = answerPrompt(), and have the condition be ``b is true''
 - Defined what ``selected for deletion'' is.
 - finish your use case 2 - yur fren, Robbinho
\end{comment}

\begin{document}

\setcounter{secnumdepth}{0}

\hbox{
	\hspace*{0.08\textwidth}
	\rule{0.5pt}{\textheight}
	\hspace*{0.001\textwidth}
	\rule{0.5pt}{\textheight}
	\hspace*{0.05\textwidth}
	\parbox[b]{0.75\textwidth}{
		{\noindent\huge\bfseries Problem Analysis \& Software Design \\}\\[2\baselineskip] % Title
		\large{
		\textbf{Group:} 9\\[\baselineskip]
		\begin{tabular}{@{}l l l l@{}}
			\textbf{Names:}& (A) Robbin de Groot  &\textbf{S-number:} &s3376508\\
			& (B) Oliver Strik  & &s3100693\\
			& (C) Nicu Ghidirimschi & & s3197395
		\end{tabular}}\\

		\vspace{6pt}
		{\large \textbf{Report:} Iteration 3 } \\[\baselineskip] % Tagline or further description
		{\large \textbf{Date:} \today } \\[4\baselineskip] % Tagline or further description
		{\large \textsc{ Prof. E.O. de Brock \& Dr. R. Smedinga }}
	\vspace{0.40\textheight} % Whitespace between the title block and the publisher
	{\Large\noindent \\ Computing Science - Year 2 \vspace{0.7cm}
	\Large\noindent \\University of Groningen \vspace{5pt}\\ \large Faculty of Science \& Engineering }}
}
\newpage

%%% index page
\tableofcontents
\vspace*{1cm}
\underline{\textbf{Notice:}} Student B (Oliver) did not manage to finish his grey and white box sequence diagrams in time. Therefore, the document is incomplete. We kindly ask the grader to take this into consideration when grading, and that student A and C (Robbin and Nicu) will not have points deducted, since all their work and effort is in the document. Thanks.

\newpage
\section{Preface}
\input{content/preface.tex}

\newpage
\input{content/intro.tex}

\newpage
\section{Use Cases}
\input{content/UCintro.tex}
% layout and sectioning from Slides week 1, page 25
\newpage
\subsection{Create and add an item - (A1)}
\input{content/usecaseA1item.tex}
\input{content/usecaseA1itemgreywhite.tex}
% \subsection{Create and add a user - (A1)}
% \input{content/usecaseA1user.tex}

\newpage
\subsection{Updating an item - (B1)}
\input{content/usecaseB1.tex}
\input{content/usecaseB1graywhite.tex}

\newpage
\subsection{Deleting items - (C1)}
\input{content/usecaseC1.tex}
\input{content/usecaseC1greywhite.tex}

\textbf{Minor clarification}: This white box sequence diagram contains only the Interface-Kernel associations that do not represent Kernel "procedures" (that is, methods that do not return anything to the interface). We justify this with the fact that these methods are represented on the Kernel level by simple atomic instructions (remove an element from the list), and are dependent on the same data as other atomic instructions, the separation of which results in overly complex and unclear design. Although this may deviate from some of the standards, we opted for it since, in our opinion, it allows us to preserve both the initially planned functionality, and the simplicity and clarity of a good design. 

\newpage
\subsection{Create a Search Service Request - (A2)}
\input{content/usecaseA2search.tex}
\subsection{Pay Search System Registration fee (sub-usecase) - (A2)}
\input{content/usecaseA2sub.tex}

% left out
% \newpage
% \subsection{Update a Search Service Request - (B2)}
% \input{content/usecaseB2.tex}

\newpage
\subsection{Reserve a book - (C2)}
\input{content/usecaseC2reserve.tex}
\input{content/usecaseC2greywhite.tex}

\newpage
\subsection{Register a regular customer - (A3)}
\input{content/usecaseA3regcust.tex}

\newpage
\subsection{View financial information for a specific period - (C3)}
\input{content/usecaseC3cmpFigures.tex}

\newpage
\section{Domain Model}
\input{content/dm.tex}

\newpage
\section{Class Diagram}
\textit{(next page)}
\input{content/cd.tex}

\newpage
\section{References}
\input{content/refs.tex}

2\end{document}