Now that we reached the end of the current iteration of our analysis and design of The AuctionHouse\textsuperscript{TM} administration system, we can show how we might deal with future request from our client.\\
First, we already have sufficient (and currently maybe superfluous) concepts in our Domain Model. These are not per se necessary in the current design, but can help clarify structure and provide a guideline for future analyses might we need to return to this project. The same goes for the Class Diagram. As we build the class diagram from the domain model, it is obvious that it also has classes available (though not yet implemented) for future implementations.\\
Most important is that we do not need to modify existing use cases or diagrams in order to adhere to new requests by our client. Therefore, we made sure that all use cases are either specific, so there is no use in changing them, or very generic, so they can be used as building blocks for newer use cases without having to rewrite parts of other use cases.\\\\
From our client, we expect to see more features coming our way. We noticed that John has gotten more and more used to the ``power of the internet'' and is willing to shift his ways to through the internet. Currently, there are barely any interactions with the system that require an internet connection, the only exception being the sending of e-mails. Every (but one) interaction is performed by staff members on request of the customers, sellers and other parties. A web based solution might be more ideal, but would require a major system overhaul. Therefore we currently do not expect this to be a requirement in the near future.